
# Time Series Analysis on Tata motors sales

```{r}
library(ggplot2)
library(tseries)
library(imputeTS)
library(forecast)
# library(greybox)
# library(smooth)
library(graphics)
library(datasets)
library(fpp2)
library(TTR)
```
## Importing data
```{r}
data = read.csv("Data/tata_data.csv")
head(data)
```
## Converting data into time-series object
```{r}
df = ts(data$Sales, start = c(2001,4), frequency = 12)
df
```

```{r}
plot(decompose(df))
```

## Decomposition of time series
```{r}
df_decom = stl(df, s.window = "p")
autoplot(df_decom)
```

## Simple exponential smoothing method
```{r}
df_ses = ses(df, h=12)

autoplot(df_ses)+ xlab("Time")+ ylab("Revenue")+theme(panel.background = element_rect(fill = "gray", colour = "red"), axis.text.x = element_text(colour = "blue"),axis.text.y = element_text(colour = "blue"), axis.title.x.bottom = element_text(colour = "red"), axis.title.y.left = element_text(color = "red"))
```



```{r}
summary(df_ses)
```

## Double exponential exponential smoothing
```{r}
df_dex = holt(df, h = 12)
df_dex
```


```{r}
autoplot(df_dex)+ xlab("Time")+ ylab("Revenue")+theme(panel.background = element_rect(fill = "gray", colour = "red"), axis.text.x = element_text(colour = "blue"),axis.text.y = element_text(colour = "blue"), axis.title.x.bottom = element_text(colour = "red"), axis.title.y.left = element_text(color = "red"))
```


```{r}
summary(df_dex)
```
## Triple(Hold Winter)exponential smoothing
```{r}
df_hw = hw(df, h=12)
df_hw
```


```{r}
autoplot(df_hw)+ xlab("Time")+ ylab("Revenue")+theme(panel.background = element_rect(fill = "gray", colour = "red"), axis.text.x = element_text(colour = "blue"),axis.text.y = element_text(colour = "blue"), axis.title.x.bottom = element_text(colour = "red"), axis.title.y.left = element_text(color = "red"))
```


```{r}
summary(df_hw)
```
## Training and testing of data for holt-Winter 
```{r}
df_train = window(df,start = c(2013,4), end = c(2021,2), frequency = 12)
df_train
```


```{r}
df_test = window(df, start = c(2021,3), frequency = 12)
df_test
```


```{r}
df_hw_train = hw(df_train,h = 12)
df_hw_train
```


```{r}
autoplot(df_hw_train)
```


```{r}
accuracy(df_hw_train, df_test)
```


```{r}
plot(df_hw_train)
lines(df_test)
```
```{r}
summary(df_hw_train)
```


```{r}
df_hw_train2 = hw(df_train, alpha = 0.62, beta = .02, gamma = .1, h=12)
plot(df_hw_train2)
lines(df_test)
```


```{r}
```

## ARIMA Model

```{r}
lags = window(df, start = c(2006,4))
lags
```


```{r}
gglagplot(lags)
```


```{r}
ggAcf(lags)
```
## Checking stationarity of the data
### H0 : Data is not stationary
### H1 : Data is stationary
```{r}
adf.test(df)
```
## First order diffrencing
```{r}
df_diff = diff(df_train,1)

autoplot(df_diff)
```


```{r}
adf.test(df_diff, alternative = "stationary" ,k=0)
```
```{r}
autoarima.fit.train = auto.arima(df_diff, trace = FALSE, stationary = TRUE, ic="bic")
autoarima.fit.train
```


```{r}
acf(df_diff)
pacf(df_diff)
```


```{r}
auto_arima_train= auto.arima(df_train, ic="bic", trace = TRUE)
```


```{r}
arima_forecast = forecast(auto_arima_train,h=12)
arima_forecast
```

```{r}
plot(arima_forecast)
lines(df, col="red")
```




## Using Moving average method 
```{r}
moving_avg = SMA(df_train,n = 3)
moving_avg
```
```{r}
forecast_ma = forecast(moving_avg,h=12)
forecast_ma
```


```{r}
plot(forecast_ma)
lines(df, col = "red")
```


```{r}
accuracy(forecast_ma, df)
```


```{r}
```


